---
title: "NFL Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: css/styles-default.css
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(shinyWidgets)
library(DT)
library(shinyjs)

# Core
library(tidyverse)
library(lubridate)

# Viz
library(plotly)

# Web Scraping
library(rvest)
library(jsonlite)


# Database
library(DBI)
library(RPostgres)

theme_set(theme_minimal())

useShinyjs(rmd = TRUE)
```


```{r}
# connect to db, grab data
con <- dbConnect(drv = RPostgres::Postgres(), user = "postgres", password = "dashsnow33", dbname = "nfl_db")

#db_list_tables(con)

dk_pts_tbl <- tbl(con, "dk_pts_tbl") %>% 
  select(everything()) %>% 
  collect()

dk_pts_tbl <- dk_pts_tbl %>% 
  mutate(team = team %>% str_to_upper(),
         opp  = opp %>% str_to_upper()) %>% 
  mutate(opp = case_when(
    opp == "OAK" ~ "LVR",
    TRUE ~ opp
  ))

```

```{r}


# Scrape fantasy pros data

fpros_flex_data <- read_csv("fpros_data.csv") %>% 
  janitor::clean_names() %>%
  select(rk, player_name, pos, opp) %>% 
  # separate(`Superflex (QB/RB/WR/TE) (Team)`,
  #          into = c("first", "last"),
  #          sep = " ") %>%
  separate(player_name, into = c("first", "last"), sep = " ") %>% 
  unite(player, c("first", "last"), sep = " ") %>% 
  mutate(
    #hold = last %>% str_detect("[.]"),
    pos = pos %>% str_extract(pattern = "[:alpha:]+")
  )

# # QB, RB, WR, TE
# fpros_flex_data <- read_html("https://www.fantasypros.com/nfl/rankings/ppr-superflex.php") %>% 
#   html_nodes("table") %>% 
#   purrr::pluck(1) %>% 
#   html_table(fill = TRUE) %>% 
#   drop_na(Rank) %>%
#   separate(`Superflex (QB/RB/WR/TE) (Team)`, into = c("first", "last"), sep = " ") %>%
#   mutate(hold = last %>% str_detect("[.]"),
#          pos = Pos %>% str_extract(pattern = "[:alpha:]+")) %>%
#   mutate(last = case_when(
#     hold == TRUE ~ last %>% str_sub(end = -3),
#     TRUE ~ last
#   )) %>% 
#   unite(player, c("first", "last"), sep = " ") %>%
#   select(rank = Rank, player, pos, opp = Opp, best = Best, worst = Worst, avg = Avg, st_dev = `Std Dev`)


# Scrape draft kings salaries
json <- jsonlite::read_json("https://api.draftkings.com/draftgroups/v1/draftgroups/43428/draftables?format=json")

players <- json %>% 
  purrr::pluck("draftables") %>% 
  map_chr(purrr::pluck("displayName")) 

salaries <- json %>% 
  purrr::pluck("draftables") %>% 
  map_dbl(purrr::pluck("salary"))


teams <- json %>% purrr::pluck("draftables") %>% 
  map_chr(purrr::pluck("teamAbbreviation"))

dk_data <- tibble(player = players, 
                  salary = salaries,
                  team = teams) %>% 
  distinct() %>% 
  mutate(player = player %>% str_trim())


# Combine fantasy pros and dk salary data
fpros_with_dk_sals_data <- fpros_flex_data %>% 
  mutate(player = case_when(
    player == "Gardner Minshew" ~ "Gardner Minshew II",
    player == "DeAndre Washington" ~ "DeAndre Washington",
    player == "Allen Robinson" ~ "Allen Robinson II",
    player == "Bennie Fowler" ~ "Bennie Fowler III",
    player == "Todd Gurley" ~ "Todd Gurley II",
    player == "D.J. Moore" ~ "DJ Moore",
    player == "Mitch Trubisky" ~ "Mitchell Trubisky",
    player == "D.J. Chark" ~ "DJ Chark Jr.",
    player == "Mark Ingram" ~ "Mark Ingram II",
    player == "Odell Beckham" ~ "Odell Beckham Jr.",
    player == "Melvin Gordon" ~ "Melvin Gordon III",
    player == "Will Fuller" ~ "Will Fuller V",
    player == "Dwayne Haskins" ~ "Dwayne Haskins Jr.",
    player == "Marvin Jones" ~ "Marvin Jones Jr.",
    player == "Henry Ruggs" ~ "Henry Ruggs III",
    player == "Ronald Jones" ~ "Ronald Jones II",
    player == "Michael Pittman" ~ "Michael Pittman Jr.",
    player == "Chris Herndon" ~ "Chris Herndon",
    player == "Laviska Shenault" ~ "Laviska Shenault Jr.",
    player == "Irv Smith" ~ "Irv Smith Jr.",
    player == "Steven Sims" ~ "Steven Sims Jr.",
    player == "Darrell Henderson" ~ "Darrell Henderson Jr.",
    player == "Van Jefferson" ~ "Van Jefferson Jr.",
    player == "John Ross" ~ "John Ross III",
    player == "A.J. Dillon" ~ "AJ Dillon",
    player == "Anthony McFarland" ~ "Anthony McFarland Jr.",
    player == "J.J. Arcega-Whiteside" ~ "JJ Arcega-Whiteside",
    player == "Benny Snell" ~ "Benny Snell Jr.",
    player == "Phillip Dorsett" ~ "Phillip Dorsett II",
    player == "Willie Snead" ~ "Willie Snead IV",
    player == "Lynn Bowden" ~ "Lynn Bowden Jr.",
    player == "Lamical Perine" ~ "La'Mical Perine",
    player == "Wayne Gallman" ~ "Wayne Gallman Jr.",
    player == "Scott Miller" ~ "Scotty Miller",
    player == "Ted Ginn" ~ "Ted Ginn Jr.",
    player == "Equanimeous S" ~ "Equanimeous St. Brown",
    player == "CJ Ham" ~ "C.J. Ham",
    player == "Donald Parham" ~ "Donald Parham Jr.",
    player == "Khadarel Hodge" ~ "KhaDarel Hodge",
    player == "D.K. Metcalf" ~ "DK Metcalf",
    TRUE ~ player
  )) %>%
  left_join(dk_data, by = "player")

```


```{r}
# get pass plays data

pass_plays <- tbl(con, "pbp_tbl") %>% 
  filter(game_date %>% between(left = lubridate::ymd("2019-09-01"), right = lubridate::ymd("2021-09-23")) &
           play_type == "pass") %>% 
  select(play_id, game_id, home_team, away_team, season_type, week, posteam, defteam, game_date, yards_gained, pass_length, pass_location, air_yards, 
         yards_after_catch, epa, passer_player_id, passer_player_name, receiver_player_id, receiver_player_name, cp, cpoe) %>% 
  collect()

pass_plays <- pass_plays %>% 
    separate(receiver_player_name, into = c("receiver_player_name", "extra"), sep = " ")

rush_plays <- tbl(con, "pbp_tbl") %>%
  filter(game_date %>% between(left = lubridate::ymd("2019-09-01"), right = lubridate::ymd("2021-09-23")) &
           play_type == "run") %>% 
  select(play_id, game_id, home_team, away_team, season_type, week, posteam, defteam, game_date, yards_gained, yardline_100, rusher_player_name, epa) %>% 
  collect()

dbDisconnect(con)

rush_plays <- rush_plays %>% 
  select(game_date, week, posteam, defteam, rusher_player_name, yards_gained, epa, yardline_100) %>% 
  drop_na()

pass_plays <- pass_plays %>% 
  select(game_date, week, posteam, defteam, receiver_player_name, pass_length, pass_location, epa, air_yards) %>% 
  drop_na()

```



Opponent Outlook
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

shinyWidgets::pickerInput(
  inputId = "select_dropdown_opp",
  label   = h4("Opponent"),
  choices = unique(dk_pts_tbl$opp) %>% sort(),
  selected = "ARI"
)

# renderText(input$select_dropdown_opp)

shinyWidgets::pickerInput(
  inputId  = "picker_weeks",
  label    = h4("Select Weeks"),
  choices  = unique(dk_pts_tbl$week),
  selected = unique(dk_pts_tbl$week),
  multiple = TRUE,
  options = list(
    `actions-box` = TRUE,
    size = 10,
    `selected-text-format` = "count > 3"
    )
)

shinyWidgets::checkboxGroupButtons(
  inputId  = "checkbox_seasons",
  label    = h4("Select Season(s)"),
  choices  = unique(dk_pts_tbl$season) %>% sort(decreasing = TRUE),
  direction = "vertical",
  selected = c(2019, 2020),
  checkIcon = list(yes = icon("ok", lib = "glyphicon"),
                   no  = NULL)
)

br()
hr()
br()

actionButton(inputId = "reset",
             label = "Reset",
             icon = icon("sync"))

observeEvent(eventExpr = input$reset, handlerExpr = {
  updatePickerInput(session = session,
                    inputId = "select_dropdown_opp",
                    selected = "ARI")
  
  updatePickerInput(
    session = session,
    inputId = "picker_weeks",
    selected = unique(dk_pts_tbl$week)
  )
  
  updateCheckboxGroupButtons(session = session,
                             inputId = "checkbox_seasons",
                             selected = "2019")
})

```

Column {data-width=350}
-----------------------------------------------------------------------
### Top Scorer vs. Opponenet per Week

```{r}
dk_pts_data_filtered <- reactive({
  dk_pts_tbl %>%
    
    filter(opp %in% input$select_dropdown_opp) %>%
    filter(week %in% input$picker_weeks) %>% 
    filter(season %in% input$checkbox_seasons) %>% 
    
    group_by(opp, season, week) %>%
    summarise(top_scorer = max(dk_pts)) %>%
    ungroup() %>%
    left_join(
      dk_pts_tbl %>%
        filter(opp %in% input$select_dropdown_opp),
      by = c("opp", "season", "week", "top_scorer" = "dk_pts")
    ) %>% 
     mutate(label_text = str_glue("Player: {str_c({first}, {last}, sep = ' ')}
                                Team: {team}
                                Salary: {salary}
                                Week: {week}
                                DK Pts: {top_scorer}"))
})

output$plot_1 <- renderPlot({
  
  dk_pts_data_filtered() %>%
    ggplot(aes(week, top_scorer)) +
    
    geom_line() +
    geom_point() +
    geom_label(aes(label = last)) +
    
    facet_wrap(~season) +
    
    labs(x = "Week", y = "DK Points")
})

plotOutput(outputId = "plot_1")
```



### Table Summary

```{r}


output$dt_output_1 <- DT::renderDataTable(
  expr = {
    dk_pts_data_filtered() %>% 
      mutate(player = str_glue("{str_c({first}, {last}, sep = ' ')}"),
             fpts   = top_scorer) %>% 
      select(player, team, opp, salary, season, week, fpts)
  },
  options = list(scrollY = "250px")
)

DTOutput(outputId = "dt_output_1")

  

```

Fantasy Pros Positional Value {data-orientation=columns}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}

shinyWidgets::checkboxGroupButtons(
  inputId  = "checkbox_pos",
  label    = h4("Select Position(s)"),
  choices  = unique(fpros_with_dk_sals_data$pos) %>% sort(),
  selected = unique(fpros_with_dk_sals_data$pos),
  direction = "vertical",
  checkIcon = list(
    yes = icon("ok", lib = "glyphicon"),
    no  = NULL
  )
)

sliderInput(
  inputId = "slider_salaries", 
  label   = h4("Salary Range"), 
  min     = 0, 
  max     = max(fpros_with_dk_sals_data$salary, na.rm = TRUE), 
  value   = c(0, max(fpros_with_dk_sals_data$salary, na.rm = TRUE)),
  step    = 100,
  round   = TRUE,
  pre     = "$"
)

shinyWidgets::pickerInput(
  inputId  = "picker_team",
  label    = h4("Select Team(s)"),
  choices  = unique(fpros_with_dk_sals_data$team) %>% sort(),
  selected = unique(fpros_with_dk_sals_data$team) %>% sort(),
  multiple = TRUE,
  options = list(
    `actions-box` = TRUE,
    size = 25,
    `selected-text-format` = "count > 3"
    )
)

br()
hr()
br()

actionButton(inputId = "reset_2",
             label = "Reset",
             icon = icon("sync"))

observeEvent(eventExpr = input$reset_2, handlerExpr = {
  updateCheckboxGroupButtons(
    session = session,
    inputId = "checkbox_pos",
    selected = unique(fpros_with_dk_sals_data$pos)
  )
  
  updateSliderInput(session = session,
                    inputId = "slider_salaries",
                    value = c(0, max(fpros_with_dk_sals_data$salary, na.rm = TRUE))
                    )
  
  updatePickerInput(
    session = session,
    inputId = "picker_team",
    selected = unique(fpros_with_dk_sals_data$team)
  )
})
```

Column {data-height=1000}
-----------------------------------------------------------------------
### Fantasy Pros Consensus Rank vs. Draft Kings Salary Rank

```{r}
fpros_with_dk_sals_data_filtered <- reactive({
  
  fpros_with_dk_sals_data %>%
    
    filter(pos %in% c(input$checkbox_pos)) %>% 
    filter(salary %>% between(left  = input$slider_salaries[1],
                              right = input$slider_salaries[2])) %>% 
    filter(team %in% c(input$picker_team))
    
})

output$dt_output_2 <- DT::renderDataTable(
  
  expr = {
    
    fpros_with_dk_sals_data_filtered() %>%
      
      mutate(Fantasy_Pros_Rank = dense_rank(rk),
             DK_Salary_Rank = dense_rank(-salary)) %>%
      mutate(Ranking_Value = DK_Salary_Rank - Fantasy_Pros_Rank) %>%
      
      select(player,
             Fantasy_Pros_Rank,
             DK_Salary_Rank,
             Ranking_Value,
             salary,
             everything()) %>% 
      arrange(Fantasy_Pros_Rank)
  },
  
  filter = "top",
  
  options = list(pageLength = 15,
                 scrollY = "650px"
                 )
  
)

DTOutput(outputId = "dt_output_2")
  
```

Pass Defense {data-orientation=columns}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
dateRangeInput(
  inputId = "date_range", 
  label   = h4("Date Range"),
  start   = ymd("2020-09-01"), 
  end     = max(pass_plays$game_date), 
  min     = min(pass_plays$game_date), 
  max     = max(pass_plays$game_date), 
  startview = "month")

```

```{r}

pp_filtered <- reactive({
  
  pass_plays %>% 
    
    filter(game_date %>% between(left  = input$date_range[1],
                                 right = input$date_range[2])) %>%
    
    select(defteam, pass_length, pass_location, epa) %>%
    drop_na()
  
  
})

```

Column {data-height=500}
-----------------------------------------------------------------------
### EPA Allowed Left Side of Field
```{r}
output$plotly_left <- renderPlotly({
  
g_left <- pp_filtered() %>%
  
  filter(pass_location %in% c("left")) %>% 
  
  group_by(defteam, pass_location) %>%
  summarize(avg_epa = epa %>% mean(),
            targets = n()) %>%
  ungroup() %>%
  
  mutate(label_text = str_glue("EPA/Att = {avg_epa}
                               Total Targets = {targets}")) %>%
  
  ggplot(aes(fct_reorder(defteam, avg_epa), avg_epa)) +
  
  geom_col(aes(text = label_text)) +
  
  coord_flip() +
  
  labs(x = "", y = "Average EPA Allowed")

ggplotly(g_left, tooltip = "text")
  
})

plotlyOutput(outputId = "plotly_left")

```

Column {data-height=500}
-----------------------------------------------------------------------
### EPA Allowed Middle of Field
```{r}
output$plotly_middle <- renderPlotly({
  
g_middle <- pp_filtered() %>%
  
  filter(pass_location %in% c("middle")) %>% 
  
  group_by(defteam, pass_location) %>%
  summarize(avg_epa = epa %>% mean(),
            targets = n()) %>%
  ungroup() %>%
  
  mutate(label_text = str_glue("EPA/Att = {avg_epa}
                               Total Targets = {targets}")) %>%
  
  ggplot(aes(fct_reorder(defteam, avg_epa), avg_epa)) +
  
  geom_col(aes(text = label_text)) +
  
  coord_flip() +
  
  labs(x = "", y = "Average EPA Allowed")

ggplotly(g_middle, tooltip = "text")
  
})


plotlyOutput(outputId = "plotly_middle")


```


Column {data-height=500}
-----------------------------------------------------------------------
### EPA Allowed Right Side of Field
```{r}
output$plotly_right <-renderPlotly({
  
g_right <- pp_filtered() %>%
  
  filter(pass_location %in% c("right")) %>% 
  
  group_by(defteam, pass_location) %>%
  summarize(avg_epa = epa %>% mean(),
            targets = n()) %>%
  ungroup() %>%
  
  mutate(label_text = str_glue("EPA/Att = {avg_epa}
                               Total Targets = {targets}")) %>%
  
  ggplot(aes(fct_reorder(defteam, avg_epa), avg_epa)) +
  
  geom_col(aes(text = label_text)) +
  
  coord_flip() +
  
  labs(x = "", y = "Average EPA Allowed")

ggplotly(g_right, tooltip = "text")
  
})



plotlyOutput(outputId = "plotly_right")


```




Receiving {data-orientation=rows}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}


dateRangeInput(
  inputId = "date_range_2", 
  label   = h4("Date Range"),
  start   = ymd("2020-09-01"), 
  end     = max(pass_plays$game_date), 
  min     = min(pass_plays$game_date), 
  max     = max(pass_plays$game_date), 
  startview = "month")

shinyWidgets::pickerInput(
  inputId  = "picker_pass_location_2",
  label    = h4("Select Pass Location(s)"),
  choices  = unique(pass_plays$pass_location) %>% sort(),
  selected = unique(pass_plays$pass_location),
  multiple = TRUE,
  options = list(
    `actions-box` = TRUE,
    size = 10,
    `selected-text-format` = "count > 3"
    )
)


br()


actionButton(inputId = "apply", label = "Apply", icon = icon(name = "play", lib = "font-awesome"))

actionButton("reset_5", label = "Reset", icon = icon("sync"))

observeEvent(eventExpr = input$reset_5, handlerExpr = {
  
  updateDateRangeInput(session = session, inputId = "date_range_2", start = ymd("2020-09-01"), end = max(pass_plays$game_date))
  
  # updatePickerInput(session = session, inputId = "picker_receiver_team", selected = unique(pass_plays$posteam))
  
  updatePickerInput(session = session, inputId = "picker_pass_location_2", selected = unique(pass_plays$pass_location))
  
  #updatePickerInput(session = session, inputId = "picker_targets", selected = 10)
  
  delay(ms = 300, expr = {
    click(id = "apply")
  })
  
})

br()
br()
br()
br()
br()
br()
hr()
br()
br()

shinyWidgets::pickerInput(
  inputId  = "picker_receiver_team",
  label    = h4("Select Team"),
  choices  = unique(pass_plays$posteam) %>% sort(),
  selected = "ARI",
  multiple = FALSE,
  options = list(
    `actions-box` = TRUE,
    size = 10,
    `selected-text-format` = "count > 3"
    )
)


```

```{r}

# Receiver Table Filter
pass_plays_filtered_2 <- eventReactive(eventExpr = input$apply, valueExpr = {
  
  pass_plays %>% 
    
    filter(game_date %>% between(left  = input$date_range_2[1],
                                 right = input$date_range_2[2])) %>%
    
    # filter(posteam %in% input$picker_receiver_team) %>% 
    
    filter(pass_location %in% input$picker_pass_location_2) %>% 
    
    select(receiver_player_name, posteam, pass_length, pass_location, epa) %>%
    drop_na() %>%
    
    group_by(receiver_player_name, posteam, pass_location) %>%
    summarize(avg_epa = epa %>% mean(),
              targets = n()) %>%
    ungroup() 
  
}, ignoreNULL = FALSE)


# Target Share Filter
target_share_filtered <- reactive({
  
  pass_plays %>%
    
    filter(game_date %>% between(
      left = lubridate::ymd("2020-09-01"),
      right = lubridate::ymd("2021-09-25")
    )) %>%
    
    filter(posteam %in% input$picker_receiver_team) %>%
    
    group_by(receiver_player_name, posteam, week) %>%
    summarize(targets = n(),
              air_yards = sum(air_yards)) %>%
    ungroup() %>%
    
    left_join(
      select(pass_plays, posteam, week, game_date, air_yards) %>%
        
        filter(
          #!is.na(air_yards),
          game_date %>% between(
            left = lubridate::ymd("2020-09-01"),
            right = lubridate::ymd("2021-09-25")
          )
        ) %>%
        
        filter(posteam %in% input$picker_receiver_team) %>% 
        
        group_by(posteam, week) %>%
        summarize(
          total_passes = n(),
          total_airyards = sum(air_yards)
        ) %>%
        ungroup(),
      by = c("posteam", "week")
    ) %>%
    
    mutate(ms_targets = targets / total_passes,
           ms_air_yards = air_yards / total_airyards,
           label_text = str_glue("Player: {receiver_player_name}
                            Target Share: {scales::percent(ms_targets, accuracy = .1)}
                            AY_Share: {scales::percent(ms_air_yards, accuracy = .1)}
                            Targets: {targets}"))
})

```

Row {data-height=1000}
-----------------------------------------------------------------------
```{r}

output$dt_output_5 <- DT::renderDataTable({
  
  pass_plays_filtered_2() %>% 
    
    arrange(desc(avg_epa))
  
  }, 
  
  filter = "top",
  
  options = list(pageLength = 50,
                 scrollY = "250px")
  
)

DTOutput(outputId = "dt_output_5")
```


Row {data-height=1000 .tabset}
-----------------------------------------------------------------------

### Market Share Targets
```{r}

output$plotly_1 <- renderPlotly({
  
  g1 <- target_share_filtered() %>%
    ggplot(aes(week, ms_targets, color = receiver_player_name)) +
    
    geom_point(aes(text = label_text)) +
    geom_line() +
    
    scale_x_continuous(breaks = c(1:17), labels = c(1:17)) +
    scale_y_continuous(labels = scales::percent) +
    
    labs(x = "Week", y = "Target Share") +
    
    theme(legend.position = "top")
  
  ggplotly(g1, tooltip = "text") %>% 
    hide_legend() %>% 
    layout(hovermode = "compare")
  
  
})

plotlyOutput(outputId = "plotly_1")



```

### Market Share Air Yards
```{r}
output$plotly_2 <- renderPlotly({
  
  g2 <- target_share_filtered() %>%
    ggplot(aes(week, ms_air_yards, color = receiver_player_name)) +
    
    geom_point(aes(text = label_text)) +
    geom_line() +
    
    scale_x_continuous(breaks = c(1:17), labels = c(1:17)) +
    scale_y_continuous(labels = scales::percent) +
    
    labs(x = "Week", y = "") +
    
    theme(legend.position = "top")
  
  ggplotly(g2, tooltip = "text") %>% 
    hide_legend() %>% 
    layout(hovermode = "compare")
  
  
})

plotlyOutput(outputId = "plotly_2")
```


Rushing {data-orientation=rows}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
shinyWidgets::pickerInput(
  inputId  = "picker_rusher_team",
  label    = h4("Select Team"),
  choices  = unique(rush_plays$posteam) %>% sort(),
  selected = "ARI",
  multiple = FALSE,
  options = list(
    `actions-box` = TRUE,
    size = 10,
    `selected-text-format` = "count > 3"
    )
)
```

```{r}
#market share carries
carry_share_filtered <- reactive({
  
  rush_plays %>%
    
    filter(game_date %>% between(
      left = lubridate::ymd("2020-09-01"),
      right = lubridate::ymd("2021-09-25")
    )) %>%
    
    filter(posteam %in% input$picker_rusher_team) %>%
    
    group_by(rusher_player_name, posteam, week) %>%
    summarize(carries = n(),
              ypc = mean(yards_gained)) %>%
    ungroup() %>%
    
    left_join(
      select(rush_plays, posteam, week, game_date, yards_gained) %>%
        
        filter(
          !is.na(yards_gained),
          game_date %>% between(
            left = lubridate::ymd("2020-09-01"),
            right = lubridate::ymd("2021-09-25")
          )
        ) %>%
        
        filter(posteam %in% input$picker_rusher_team) %>% 
        
        group_by(posteam, week) %>%
        summarize(
          total_carries = n()
        ) %>%
        ungroup(),
      by = c("posteam", "week")
    ) %>%
    
    mutate(ms_carries = carries / total_carries,
           label_text = str_glue("Player: {rusher_player_name}
                            Carry Share: {scales::percent(ms_carries, accuracy = .1)}
                            YPC: {ypc}"))
})


# market share goalline
goalline_filtered <- reactive({
  
  rush_plays %>%
    
    filter(game_date %>% between(
      left = lubridate::ymd("2020-09-01"),
      right = lubridate::ymd("2021-09-25")
    )) %>%
    
    filter(yardline_100 <= 5) %>% 
    
    filter(posteam %in% input$picker_rusher_team) %>%
    
    group_by(rusher_player_name, posteam, week) %>%
    summarize(carries = n(),
              ypc = mean(yards_gained)) %>%
    ungroup() %>%
    
    left_join(
      select(rush_plays, posteam, week, game_date, yards_gained, yardline_100) %>%
        
        filter(
          !is.na(yards_gained),
          yardline_100 <= 5,
          game_date %>% between(
            left = lubridate::ymd("2020-09-01"),
            right = lubridate::ymd("2021-09-25")
          )
        ) %>%
        
        filter(posteam %in% input$picker_rusher_team) %>% 
        
        group_by(posteam, week) %>%
        summarize(
          total_carries = n()
        ) %>%
        ungroup(),
      by = c("posteam", "week")
    ) %>%
    
    mutate(ms_goalline = carries / total_carries,
           label_text = str_glue("Player: {rusher_player_name}
                            Carry Share Inside 5: {scales::percent(ms_goalline, accuracy = .1)}
                            Carries Inside 5: {carries}"))
})
```

Row {data-height=1000}
-----------------------------------------------------------------------

### Market Share Carries
```{r}
output$plotly_3 <- renderPlotly({
  
  g3 <- carry_share_filtered() %>%
    ggplot(aes(week, ms_carries, color = rusher_player_name)) +
    
    geom_point(aes(text = label_text)) +
    geom_line() +
    
    scale_x_continuous(breaks = c(1:17), labels = c(1:17)) +
    scale_y_continuous(labels = scales::percent) +
    
    labs(x = "Week", y = "") +
    
    theme(legend.position = "top")
  
  ggplotly(g3, tooltip = "text") %>% 
    hide_legend() %>% 
    layout(hovermode = "compare")
  
  
})

plotlyOutput(outputId = "plotly_3")
```

Row {data-height=1000}
-----------------------------------------------------------------------

### Market Share Carries Inside 5 Yardline
```{r}
output$plotly_4 <- renderPlotly({
  
  g3 <- goalline_filtered() %>%
    ggplot(aes(week, ms_goalline, color = rusher_player_name)) +
    
    geom_point(aes(text = label_text)) +
    geom_line() +
    
    scale_x_continuous(breaks = c(1:17), labels = c(1:17)) +
    scale_y_continuous(limits = c(0:1), labels = scales::percent) +
    
    labs(x = "Week", y = "") +
    
    theme(legend.position = "top")
  
  ggplotly(g3, tooltip = "text") %>% 
    hide_legend() %>% 
    layout(hovermode = "compare")
  
  
})

plotlyOutput(outputId = "plotly_4")
```